Containers and R---the Rockerverse and beyond

### 2020-01-16 manuscript.Rmd
extend jupyter docker stack description

The [**Jupyter Docker Stacks** project](https://github.com/jupyter/docker-stacks/) are a set of ready-to-run Docker images containing Jupyter applications and interactive computing tools \citep{project_jupyter_jupyter_2018}.
The `jupyter/r-notebook` image includes R and "popular packages", and R is also included in the catchall `datascience-notebook` image\footnote{\href{https://jupyter-docker-stacks.readthedocs.io/en/latest/using/selecting.html}{https://jupyter-docker-stacks.readthedocs.io/en/latest/using/selecting.html}}.
For example, these images allow users to quickly start a Jupyter Notebook server locally or build their own specialised images on top of stable toolsets.

>>>>

The [**Jupyter Docker Stacks**](https://github.com/jupyter/docker-stacks/) project are a set of ready-to-run Docker images containing Jupyter applications and interactive computing tools \citep{project_jupyter_jupyter_2018}.
The `jupyter/r-notebook` image includes R and "popular packages", and naturally also the IRKernel ([https://irkernel.github.io/](https://irkernel.github.io/)), an R kernel for Jupyter so that Jupyter Notebooks can contain R code cells. 
R is also included in the catchall `jupyter/datascience-notebook` image\footnote{\href{https://jupyter-docker-stacks.readthedocs.io/en/latest/using/selecting.html}{https://jupyter-docker-stacks.readthedocs.io/en/latest/using/selecting.html}}.
For example, these images allow users to quickly start a Jupyter Notebook server locally or build their own specialised images on top of stable toolsets.
The R installation is installed using the Conda package manager, which can manage environments for various programming languages, pinning both the R version and the versions of R packages\footnote{See `jupyter/datascience-notebook` `Dockerfile` at \href{https://github.com/jupyter/docker-stacks/blob/master/datascience-notebook/Dockerfile#L47}{https://github.com/jupyter/docker-stacks/blob/master/datascience-notebook/Dockerfile#L47}.}.
